---
title: "Illusion Game Validation (Study 3)"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "sampling",
  brms.backend = "cmdstanr"
)

cache <- TRUE
runModels <- FALSE
bestModels <- FALSE
fig.width <- see::golden_ratio(7)
fig.height <- 7

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.path = "./figures/",
  fig.width = fig.width,
  fig.height = fig.height
)
```


# Introduction


The goal of study 3 was to...

We have to keep in mind that individual scores are the result of several layers of simplification: 1) the individual coefficient is that of simpler models that sometimes do not perfectly capture the underlying dynamics (especially in the case of ...), 2) the structural equation model from which they are obtained is also constructed on layers of abstractions. Though, as we have seen, these indices to relate to empirical scores, such as the average error rate and RT in the task.

# Methods

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggdist)
library(ggside)
library(easystats)
library(patchwork)
library(brms)

# Variables
DVs <- c("Delboeuf" = "#2196F3", 
         "Ebbinghaus" = "#3F51B5", 
         "RodFrame" = "#F44336", 
         "VerticalHorizontal" = "#FF5722", 
         "Zollner" = "#FF9800", 
         "White" = "#9E9E9E", 
         "MullerLyer" = "#4CAF50", 
         "Ponzo" = "#009688", 
         "Poggendorff" = "#795548", 
         "Contrast" = "#607D8B", 
         "I" = "#9C27B0")

# Load data
dfsub <- read.csv("../data/study3.csv") |>
  mutate(
    Screen_Refresh = as.numeric(Screen_Refresh),
    Education = fct_relevel(Education, "High School", "Bachelor", "Master", "Doctorate", "Other", "Prefer not to Say")
  ) |> 
  datawizard::standardise(select=names(DVs))

dflong <- dfsub |> 
  pivot_longer(all_of(names(DVs)), names_to = "Index", values_to = "Score")
# plot(estimate_density(dfsub[DVs]))
```


## Results 


### Contextual

#### Screen Size

```{r message=FALSE, warning=FALSE, cache=cache}
preds <- data.frame()
for(i in names(DVs)) {
  model <- brms::brm(paste0(i, " ~ s(Screen_Size)"), data=dfsub, algorithm = "meanfield", refresh=0)
  param <- bayestestR::describe_posterior(as.data.frame(model))
  
  pred <- estimate_relation(model, length=50)
  pred$Index <- i
  pred$sig <- estimate_slopes(model, trend = "Screen_Size")$pd
  preds <- rbind(preds, pred)
  
  if(any(pred$sig > .95)) {
    print(i)
  }
}

preds |> 
  mutate(sig = format_pd(sig, stars_only = TRUE),
         sig = ifelse(sig == "", "NS", sig)) |> 
  ggplot(aes(x = Screen_Size, y = Predicted)) +
  geom_point2(data=dflong, aes(y = Score, color= Index), alpha=0.1, size=2) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1.5)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "dashed", "**" = "solid")) +
  scale_color_manual(values = DVs) +
  coord_cartesian(ylim = c(-2.5, 2.5)) +
  theme_modern() +
  labs(y = "Illusion Sensitivity", x = "Screen Size") +
  ggside::geom_xsidedensity(data=dfsub, fill ="grey", color = "white") +
  ggside::geom_ysidedensity(data=dflong, aes(y=Score, color = Index)) +
  ggside::theme_ggside_void() 
```

#### Refresh Rate

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
preds <- data.frame()
for(i in DVs) {
  model <- brms::brm(paste0(i, " ~ poly(Screen_Refresh, 2)"), data=dfsub, algorithm = "meanfield", refresh=0)
  param <- bayestestR::describe_posterior(as.data.frame(model))
  
  pred <- estimate_relation(model, length=50)
  pred$Index <- i
  pred$sig <- max(param$pd[2:3])
  preds <- rbind(preds, pred)
  
  if(any(max(param$pd[2:3]) > .95)) {
    print(i)
  }
}

preds |> 
  mutate(sig = format_pd(sig, stars_only = TRUE),
         sig = ifelse(sig == "", "NS", sig)) |> 
  ggplot(aes(x = Screen_Refresh, y = Predicted)) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1.5)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "dashed", "**" = "solid"))
```


### Demographics

#### Sex

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
params <- data.frame()
for(i in DVs) {
  model <- lm(paste0(i, " ~ Sex"), data=dfsub)
  param <- parameters::parameters(model)
  param$Index <- i
  param$ymiddle <- param$Coefficient[1] + diff(param$Coefficient) / 2
  params <- rbind(params, as.data.frame(param[2, ]))
  if(param$p[2] < .05) {
    print(i)
  }
}

data <- dfsub |> 
  pivot_longer(all_of(DVs), names_to = "Index", values_to = "Score") |> 
  mutate(Index = fct_relevel(Index, arrange(params, p)$Index))

data |> 
  ggplot(aes(x = Index, y = Score)) +
  stat_slab(data=filter(data, Sex == "Male"), aes(fill = Sex), side = "right", scale = 0.5, position = "dodge") +
  stat_slab(data=filter(data, Sex == "Female"), aes(fill = Sex), side = "left", scale = 0.5, position = "dodge") +
  stat_pointinterval(aes(group = Sex), point_interval = "mean_qi",, position = "dodge") +
  geom_text(data = mutate(params, sig = insight::format_p(p, stars_only = TRUE)), aes(label = sig, y = ymiddle))
```


#### Ethnicity

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
params <- data.frame()
for(i in DVs) {
  model <- lm(paste0(i, " ~ Ethnicity"), data=dfsub)
  param <- estimate_contrasts(model, contrast = "Ethnicity")
  param$Index <- i
  params <- rbind(params, as.data.frame(param[2, ]))
  if(any(param$p < .05)) {
    print(i)
  }
}
```



#### Education

```{r message=FALSE, warning=FALSE, cache=cache}
preds <- data.frame()
for(i in DVs) {
  model <- brms::brm(paste0(i, " ~ mo(as.numeric(Education))"), data=filter(dfsub, !Education %in% c("Other", "Prefer not to Say")), algorithm = "meanfield", refresh=0)
  param <- bayestestR::describe_posterior(as.data.frame(model)["bsp_moas.numericEducation"])
  
  pred <- estimate_relation(model)
  pred$Index <- i
  pred$sig <- param$pd
  preds <- rbind(preds, pred)
  
  if(any(param$pd > .95)) {
    print(i)
  }
}

preds |> 
  mutate(sig = format_pd(sig, stars_only = TRUE),
         sig = ifelse(sig == "", "NS", sig)) |> 
  ggplot(aes(x = Education, y = Predicted)) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1.5)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "dashed", "**" = "solid"))
```


#### Age

```{r message=FALSE, warning=FALSE, cache=cache}
sig <- list()
preds <- data.frame()
for(i in DVs) {
  model <- brms::brm(paste0(i, " ~ poly(Age, 2)"), data=dfsub, algorithm = "meanfield", refresh=0)
  param <- bayestestR::describe_posterior(as.data.frame(model))
  
  pred <- estimate_relation(model, length=50)
  pred$Index <- i
  pred$sig <- max(param$pd[2:3])
  preds <- rbind(preds, pred)
  
  if(any(max(param$pd[2:3]) > .95)) {
    print(i)
  }
}

preds |> 
  mutate(sig = format_pd(sig, stars_only = TRUE),
         sig = ifelse(sig == "", "NS", sig)) |> 
  ggplot(aes(x = Age, y = Predicted)) +
  geom_line(aes(color = Index, group = Index, linetype = sig, size = sig)) +
  scale_size_manual(values = c("NS" = 0.5, "*" = 1, "**" = 1.5)) +
  scale_linetype_manual(values = c("NS" = "dotted", "*" = "dashed", "**" = "solid"))
```

### Personality

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
r <- correlation::correlation(
  datawizard::data_select(dfsub, DVs),
  select(dfsub, starts_with("IPIP") & !ends_with("_SD")),
  p_adjust = "none",
  sort=TRUE
)


r |>
  mutate(label = paste0(format_value(r, zap_small = TRUE), insight::format_p(p, stars_only=TRUE))) |> 
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r)) +
  geom_text(aes(label=label), size=3) +
  scale_alpha_continuous(range = c(1, 0.5)) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  # facet_wrap(~Illusion_Type, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

